Delone lattice studies in \CIII, the space of three complex variables

### 2023-03-13 C3/C3.tex
changes from HJB & FCB

	~\citeasnoun{andrews2019b} chose to 
	represent the Selling scalars in the space \SVI{},
	\Svec{} (defined in the order above), 
	as a way to create a metric space
	for the measurement of the distance between lattices. 
	~\citeasnoun{andrews2019b} also considered the representation 
	of this space as the
	space of three complex dimensions, \CIII{} or 
	{$\{c_1$}, {$c_2$}, {$c_3\}$}.

	In \CIII{}, in terms of the Selling scalars, 
	a vector is defined as \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of~\citeasnoun{Delaunay1932}
	(opposite in terms of the Bravais tetrahedron of scalars) (see~\citeasnoun{andrews2019a}).
	As a mnemonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).
	Additionally, each complex term uses all 
	four 3-space vectors; for example, $c_1$ is ($b \cdot c$, $a \cdot d$).

	~\citeasnoun{andrews2019b} considered the matrix representations 
	of the reflections in \CIII{} (and in \SVI{}). 
	This paper describes the boundary transformations 
	at the edges of the fundamental	unit of \CIII{}
	and also a graphical presentation. 
	In \SVI{}, the fundamental unit is the all negative orthant, 
	which contains only, and all, of the reduced cells. 
	In \SVI{} and \CIII{}, 
	the boundaries located where any \SVI{} scalar 
	(or correspondingly in \CIII{}, a real or imaginary part) 
	equals to zero.

@@

	Complex numbers will be represented 
	in Cartesian format $(x,y)$, 
	where $x$ is the real part and
	$y$ is the imaginary part.

	We will represent a vector 
	in \CIII{} by \{$(x_1,y_1)$, $(x_2,y_2)$, $(x_3, y_3)$\} 
	as an alternative to  \{(\si,\siv ), (\sii,\sv),(\sii,\svi)\}.

@@

	The standard representation of the identity operation is

@@

	The identity in \CIII{} can also be written:

@@

\begin{figure}
	\includegraphics[width=1.0\textwidth]{5_21}
	\caption{The PLA2 unit cells Niggli-reduced, and five copies were perturbed 10\%
		orthogonally to \SVI{} vector. }
	\label{fig5}
\end{figure}

@@

The transformation matrices shown above demonstrate the 
considerable regularity of Selling reduction, as used by 
Delaunay (1932); The reduction operations of Niggli 
reduction \cite{Niggli1928} are more complex. 
While all the boundaries of the non-positive 
orthant of \SVI{} are essentially the same (and 
related by reflections), the boundaries formed in 
Niggli reduction are of multiple types, and the fundamental unit 
of the space representing Niggli-reduced cells (\GVI{}, see \citeasnoun{Andrews2014}) is non-convex.

@@

	\bibliographystyle{iucr}

>>>>

	~\citeasnoun{andrews2019b} chose to 
	represent the Selling scalars in the space \SVI{},
	\Svec{} (defined in the order above), 
	as a way to create a metric space
	for the measurement of the distance between lattices. 
	They also considered the representation 
	of this space as the
	space of three complex dimensions, \CIII{} or 
	{$\{c_1$}, {$c_2$}, {$c_3\}$}.

	In \CIII{}, in terms of the Selling scalars, 
	a vector is defined as \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of~\citeasnoun{Delaunay1932}
	(opposite in terms of the Bravais tetrahedron of scalars) (see~\citeasnoun{andrews2019a}).
	As a mnemonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).
	Additionally, each complex term uses all 
	four three-space vectors; for example, $c_1$ is ($b \cdot c$, $a \cdot d$).

	~\citeasnoun{andrews2019b} considered the matrix representations 
	of the reflections in \CIII{} (and in \SVI{}). 
	This paper describes the boundary transformations 
	at the edges of the fundamental	unit of \CIII{}
	and also a graphical presentation. 
	In \SVI{}, the fundamental unit is the all negative orthant, 
	which contains only, and all of, the reduced cells. 
	In \SVI{} and \CIII{}, 
	the boundaries located where any \SVI{} scalar 
	(or correspondingly in \CIII{}, a real or imaginary part) 
	equals zero.

@@

	Complex numbers are represented 
	in Cartesian format $(x,y)$, 
	where $x$ is the real part and
	$y$ is the imaginary part.

	We represent a vector 
	in \CIII{} by \{$(x_1,y_1)$, $(x_2,y_2)$, $(x_3, y_3)$\} 
	as an alternative to  \{(\si,\siv ), (\sii,\sv),(\sii,\svi)\}.

@@

	The standard representation of the identity operation is\\

@@

	The identity in \CIII{} can also be written:\\

@@

\begin{figure}
	\includegraphics[width=1.0\textwidth]{5_21}
	\caption{The PLA2 unit cells, Niggli-reduced, and five copies were perturbed 10\%
		orthogonally to \SVI{} vector. }
	\label{fig5}
\end{figure}

@@

The transformation matrices shown above demonstrate the 
considerable regularity of Selling reduction, as used by 
Delaunay (1932). The reduction operations of Niggli 
reduction \cite{Niggli1928} are more complex. 
While all the boundaries of the non-positive 
orthant of \SVI{} are essentially the same (and 
related by reflections), the boundaries formed in 
Niggli reduction are of multiple types, and the fundamental unit 
of the space representing Niggli-reduced cells (\GVI{}, see \citeasnoun{Andrews2014}) is non-convex.

@@

	\bibliographystyle{iucrit}
